# Acute Pain Management in the Perioperative Setting (2012)

```{r, echo = FALSE, include = FALSE}
library(tidyverse)
library(janitor)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, options(knitr.kable.NA = '', dev = 'svg'), knitr.graphics.error = FALSE,
                      warning = FALSE, message = FALSE, fig.align = "left", comment = NA)
opt_font <-  c("Source Sans Pro")
opt_boot <- c("striped", "hover", "condensed")

recs_dat <- readxl::read_xlsx("_data/pp_recs_all.xlsx", sheet = "Guidelines", range = "A1:F485")

pain_recs <- recs_dat |> 
    filter(str_detect(parameter, "Pain"))

sections <- pain_recs |>
  tabyl(rec_title) |>
  select(rec_title)

temp <- pain_recs |>
  tabyl(rec_title)

recs_display <- function(recs_list, sec_list){
recs_list |> 
    filter(rec_title == sec_list) |> 
    select(rec, evidence) |> 
    kbl( 
    booktabs = T, align = c("lc"), escape = FALSE, # format = "latex",
    col.names = c("Recommendation", "Evidence")
  ) |> 
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") |> 
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") |> 
  column_spec(1, width = "40em") |> 
  column_spec(2, width = "8em") |> 
  footnote(
    general = "Categories of evidence: ",
    alphabet = c("Strength of evidence or category of recommentation"
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )
}


```

## Geriatric Patients

```{r}
recs_display(pain_recs, "Geriatric Patients")
```

## Institutional Policies and Procedures for Providding Perioperative Pain Management

```{r}
recs_display(pain_recs, "Institutional Policies and Procedures for Providding Perioperative Pain Management")
```

## Multimodal and Multidisciplinary Interventions

```{r}
recs_display(pain_recs, "Multimodal and Multidisciplinary Interventions")
```

## Multimodal Techniques for Pain Management

```{r}
recs_display(pain_recs, "Multimodal Techniques for Pain Management")
```

## Other Patients

```{r}
recs_display(pain_recs, "Other Patients")
```

## Patient Evaluation

```{r}
recs_display(pain_recs, "Patient Evaluation")
```

## Pediatric Patients

```{r}
recs_display(pain_recs, "Pediatric Patients")
```

## Perioperative Techniques for Pain Management

```{r}
recs_display(pain_recs, "Perioperative Techniques for Pain Management")
```

## Preoperative Evaluation of the Patient

```{r}
recs_display(pain_recs, "Preoperative Evaluation of the Patient")
```

## Preoperative Preparation of the Patient

```{r}
recs_display(pain_recs, "Preoperative Preparation of the Patient")
```

## Single Modality Interventions

```{r}
recs_display(pain_recs, "Single Modality Interventions")
```
